---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RTLappOptions

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/risktoollib/RTLappOptions/workflows/R-CMD-check/badge.svg)](https://github.com/risktoollib/RTLappOptions/actions)
[![Travis build status](https://travis-ci.com/risktoollib/RTLappOptions.svg?branch=master)](https://travis-ci.com/risktoollib/RTLappOptions)
<!-- badges: end -->

***Part of a series of Shiny Apps to support education of risk managers and trading analysts in Universities and commodity-trading enterprises.***

This app is designed and shared publicly to support education in options trading and risk management. 

Whilst most textbooks and courses focus on individual instruments, managing risk at the portfolio level introduces a complex interaction of sensitivities. Being able to simulate the risk profile outside a narrow band of market movements is an integral part of internalizing the knowledge required to operate at Enterprise level.

## Installation

You can install the development version of `RTLappOptions` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("risktoollib/RTLappOptions")
```

## Running the app

```{r, eval=FALSE}
library(RTLappOptions)
RTLappBonds::run_app()
```

